---
title: "R Notebook"
output: html_notebook
---

# R - the final frontier, bonfire 129 final lecture

### Goals:

Intake data from kaggle

<https://www.kaggle.com/datasets/saadharoon27/hr-analytics-dataset>

analyse it

clean and transform,

model/stat test

visualize

## I. Intake

```{r}
# Tidyverse is the primary package for processing
library(tidyverse)

# using the underscore for tibble formatted data
df<- read_csv('HR_Analytics.csv')

#open the file in a new view
view(df)
```

## II. Clean and transform

### a - update column names

```{r}
# reserved for regex method from chat gpt
# 

names(df)
```

```{r}
names(df) <- gsub("([a-z0-9])([A-Z])", "\\1_\\2", names(df))
names(df) <- names(df) %>% tolower()
view(df)
```

### b - clean business travel data? (change dashes to underscores)

### c - implicit boolean column

```{r}
# Checking column data types -- STR == STRUCTURE
str(df)
```

```{r}
# changing column types to be bool
df <- df %>% mutate(over18 = case_when(over18 == "Y"~ "TRUE", over18 == "N" ~ "FALSE"))


df <- df %>% mutate(attrition = case_when(attrition == "Yes"~ "TRUE", attrition == "No" ~ "FALSE"))

df <- df %>% mutate(overtime = case_when(over_time == "Yes"~ "TRUE", over_time == "No" ~ "FALSE"))


```

```{r}
view(df)

```

### d - null values

```{r}
colSums(is.na(df))
```

\*\*check data to see if cols with null values is important to our hypothesis\*\*

SQL will be fine with null values as long as it's not a primary/foreign key column (not sure why this came up)

Kali suggested doing a correlation coefficient test to see if the column with null values is correlated to our dependent/independent variables

### e - start thinking about dependent/independent variables to formulate the null/alternative hypothesis

$Ho:$ Education level has no impact on

$Ha:$ Salary and education have a statistical relationship to one another

## Step 3: Explore

-   View the relationship between education level and their montly_income

-   View distribution of the target column, or our dependant variable

-   View distribution fo the independent variable.

-   View the relationship between the month_income and all other variables as well(cor)

```{r}
ggplot(data = df, aes(x=education, y=monthly_income)) +
  geom_point()
```

```{r}
cor(df$education, df$monthly_income) * 100
```

## Step 4: Analyze

```{r}
model <- lm(df$monthly_income ~ df$education)
model
```

```{r}
summary(model)
```
